### 2021-04-06 site/03-meeting.Rmd
update site

We describe our methods in this chapter.

>>>>

## March 10, 2021 - Week 2

1. Human subject experiment and Monash permission
    - There is a workshop in May
2. Use simulated data to set up an experiment
3. Check out Gallery of graphs (a name yan ... not sure)
4. The experiment could start from residual plot
7. Q-Q plot could also be considered
8. A revelant research - residual calculation by kaiwen - master project
9. Use Appen survey to collect data
10. Build a Github to-do list, meeting record and summary of the literature
11. There may be some development in the theory by Nancy Reid - theoretical statistician (recent work)
12. Consider using Kears to build a computer vision model

## March 17, 2021 - Week 3

1. Read Susan Vanderplas's personal website to find additional information
2. Check out NUMBAT residual plot comparision - summer-vis-inf : Aarathy Babu - code examples
3. Read human subject premission examples (sent by Di)
4. Check out top-up application
5. Consider to use `Edibble` to set up the experiment
6. Build the PhD repo
7. Consider to use non-shiny framework

## March 21, 2021 - Week 4

1. A short meeting - late for 30 minutes
2. Aarathy introduces her repo

## March 28, 2021 - Week 5

1. Discuss the options of building a alternative hypothesis in residual plot
2. AR, heterogeneity of variance, endogeneity, skewness, exp distribution, poisson distribution and missing covariance
3. Choice of plot design (loess or $y=0$ line), number of lineup (5~15), number of observations
4. Use flow chart to illustrate the choices
5. Literature review - check previous designs
6. Build bookdown to track records
